### 2017-09-22 proposal/draft.tex
shvenv

    \item \url{http://journals.ametsoc.org/doi/abs/10.1175/JAS-D-11%
        -097.1} has already studied to some extent in atmospheres, weakly
        nonlinear regime
        % sutherland 2011
\end{itemize}

>>>>

    \item \url{http://journals.ametsoc.org/doi/abs/10.1175/JAS-D-11%
        -097.1} has already studied to some extent in atmospheres, weakly
        nonlinear regime
        % sutherland 2011

    \item LIGO seems to have detected neutron star binaries
        (\url{https://www.sciencenews.org/article/rumors-swirl-ligo-snagged-%
        gravitational-waves-neutron-star-collision},
        \url{http://news.nationalgeographic.com/2017/08/new-%
        gravitational-waves-neutron-stars-ligo-space-science/}), white dwarf
        waveforms crucial!

    \item Do WD GW papers account for this?
\end{itemize}
